### 2024-02-19 author-kit-CVPR2024-v2/sec/1_intro.tex
Finished Proposal Content

%-------------------------------------------------------------------------
\subsection{Existing Attempts}

Several existing attempts have been made to tackle the challenge of learning dance from online 
videos, each with its own approach and limitations. One such approach involves platforms that 
generate reskinned versions of dance performances, offering visual references for users. These 
platforms overlay graphics or animations onto the original video, highlighting key movements or 
positions to provide guidance. While these reskinned versions serve as visual aids, they 
typically do not offer active instruction or detailed breakdowns of the dance steps. As a result, 
users may struggle to fully grasp the nuances and intricacies of the movements, limiting the 
effectiveness of this approach as a learning tool.

@@

\subsection{Useful Techniques}

Several computer vision techniques offer promising avenues for addressing the challenge of learning 
dance from online videos by providing deeper insights into the dynamics and nuances of dance 
movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of movements, including depth information. This 
 allows for a more accurate and detailed representation of the dancer's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 dance choreographies.

@@

>>>>

%-------------------------------------------------------------------------
\subsection{Existing Attempts}
Several existing attempts have been made to tackle the challenge of learning dance from online 
videos, each with its own approach and limitations. One such approach involves platforms that 
generate reskinned versions of dance performances, offering visual references for users. These 
platforms overlay graphics or animations onto the original video, highlighting key movements or 
positions to provide guidance. While these reskinned versions serve as visual aids, they 
typically do not offer active instruction or detailed breakdowns of the dance steps. As a result, 
users may struggle to fully grasp the nuances and intricacies of the movements, limiting the 
effectiveness of this approach as a learning tool.

@@

\subsection{Useful Techniques}
Several computer vision techniques offer promising avenues for addressing the challenge of learning 
dance from online videos by providing deeper insights into the dynamics and nuances of dance 
movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of movements, including depth information. This 
 allows for a more accurate and detailed representation of the dancer's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 dance choreographies.

@@

\subsection{Challenges}
Several challenges arise from attempting this project. One is the quality of input data, which 
encompasses various factors such as lighting, angles, occlusions, frame rates, and blurring. These 
factors can significantly impact the accuracy of movement analysis, as they can obscure or distort 
key visual information needed for understanding dance movements. Addressing these challenges may 
require the development of robust computer vision algorithms capable of handling noisy or low-quality 
video data, as well as techniques for preprocessing and enhancing the visual information to improve 
analysis accuracy.

Moreover, handling interactions between multiple dancers in an ideal video presents additional 
complexities in accurately capturing and representing dance movements. In many dance performances, 
especially group or partner dances, dancers may interact with each other in complex ways, such as 
lifts, partner work, or coordinated movements. Capturing these interactions and accurately 
representing them in the analysis poses challenges for computer vision algorithms, as they must be 
able to differentiate between individual dancers and track their movements independently while also 
accounting for their interactions with others. Addressing this challenge may require the development 
of advanced tracking and segmentation techniques capable of accurately identifying and tracking 
multiple dancers in a crowded or dynamic environment.

Overall, addressing these challenges requires a multidisciplinary approach that combines expertise 
in computer vision, dance analysis, and human-computer interaction. By developing robust algorithms, 
incorporating domain-specific knowledge, and leveraging advanced techniques for handling complex 
visual data, it is possible to create a tool that effectively supports learning dance from online 
videos using computer vision. However, continued research and development efforts are needed to 
overcome these challenges and realize the full potential of computer vision technology in the 
field of dance education.

\subsection{Technical Gap}
The primary aim of this project is to reduce the technical gap between online dance learning resources and 
effective dance instruction. By enabling the correspondence between individuals with different body proportions 
captured from various angles, this tool seeks to enhance the accessibility and inclusivity of dance education. 
This interdisciplinary endeavor involves collaboration between experts in dance, biomechanics, and computer 
vision, with computer vision providing quantitative analysis capabilities to enhance the understanding and 
teaching of dance movements.

In conclusion, developing a tool for learning dance from online videos using computer vision holds 
great potential for revolutionizing dance education and making it more accessible to a wider 
audience. By leveraging advanced computer vision techniques and interdisciplinary collaboration, 
this project aims to bridge the gap between online dance resources and effective dance instruction, 
ultimately empowering individuals to learn and appreciate dance in new and innovative ways.
